---
title: "Tidymodels Regression"
output: html_notebook
---

# tidymodels - use this framework
provides a nice clean framework for building different model types. We'll focus on regression here but realize it can do supervised, unsupervised, classification and other tasks as well. 

## Libraries 
we need two new libraries 

tidymodels - model building framework
vip - variable importance 

but good to have lubridate, skimr and tidyverse


```{r}
library(tidyverse)
library(tidymodels)
library(lubridate)
library(skimr)
library(vip)
```


## Data
```{r}
wake <- read_csv("data/wake_county.csv")

head(wake)
```
```{r}
wake %>% 
  skim_without_charts()
```


```{r}
wake <- wake %>%
  mutate(zip_code = factor(zip_code)) %>%
  mutate(across(is.character, factor))
```


```{r}
library(recipes)
library(rsample)
library(modeldata)

set.seed(42)
train_test_split <- initial_split(wake)

train <- training(train_test_split)
test <- testing(train_test_split)
```



# Intial Recipe 

Formula is simply target ~ var1 + var2 ... varN or target ~ . all the varaibles 

update_role: ignore variables 
step_mode/median/mean impute: deal with missing values 
step novel - 	deal with New/Novel factor levels 
step center - make numbers to have a mean of 0 
step scale  - make numbers to have a sd of 1 
step_zv() - Zero Variance Filter
step_dummy - make 0/1 of factor levels 




```{r}
rec_obj <- recipe(sale_price ~ ., data = train) %>%
  update_role(pin_num,owner, site_address, city_state_zip, new_role = "id variable") %>% 
  step_modeimpute(zip_code) %>%
  step_meanimpute(heatedarea) %>%
  step_mutate(home_age = 2021 - year_built, 
              sale_age = 2021 - year(sale_date)) %>%
  update_role(year_built,sale_date, new_role = "date variables" ) %>%
  step_novel(all_nominal())  %>%
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes()) %>%
  step_dummy(zip_code,city) 
  
rec_obj
```

## Bake your recipe 
```{r}
bake_train <- bake(rec_obj %>% prep(), train)
bake_test  <- bake(rec_obj %>% prep(), test)
```

## Model Spec 

```{r}
model_obj <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

```

## Workflow

```{r}
workflow_spec <- workflow() %>%
  add_recipe(rec_obj) %>%
  add_model(model_obj) 

workflow_fit <- workflow_spec %>%
  fit(data= train)
```


## Inspect workflow 
```{r}
workflow_fit$fit
```

```{r}
tidy(pull_workflow_fit(workflow_fit) )%>%
  mutate(across(is.numeric,round,3))
```

## Metrics

```{r}

bind_cols(predict(workflow_fit, train), train) %>%
  mutate(part = "train") -> train_predict 

bind_cols(predict(workflow_fit, test), test) %>%
  mutate(part = "test") -> test_predict 

bind_rows(train_predict, test_predict) %>%
  group_by(part) %>%
  metrics(truth = sale_price, estimate = .pred) %>%
  mutate(.estimate = round(.estimate,3)) %>%
  pivot_wider(id=part, names_from = .metric, values_from=.estimate)

```



## Variable Importance 
```{r}
vip(pull_workflow_fit(workflow_fit))
```

## Predictions 

Top n, right vs wrong 

```{r}
test_predict %>%
  mutate(res = sale_price - .pred) %>%
  slice_max(abs(res),n=10)

test_predict %>%
  mutate(res = sale_price - .pred) %>%
  slice_min(abs(res),n=10)
```





